---
title: "HW 6"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(mgcv)
library(rvest)
library(httr)
library(modelr)

library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


# Problem 2 

```{r, echo = FALSE, warning = FALSE, message = FALSE}
homicide_rawdf = read_csv("./data/homicide-data.csv")
```
_Description of raw data_ This dataset overviews demographic and geographic data for homicide victims across various cities in the United States. It has `n rows(homicide_rawdf)` rows and `ncols(homicide_rawdf)` columns.

Steps: 

1. Cleaned the data

```{r, echo = FALSE}
homicide_cleandf = 
  homicide_rawdf %>% 
  mutate(
    city_state = str_c(city,", ", state), 
    solved = case_when(disposition == "Closed by arrest" ~ 1,
                          disposition != "Closed by arrest" ~ 0)
  ) %>% 
  filter(
    city_state != "Dallas, Tx", 
    city_state != "Phoenix, AZ",
    city_state != "Kansas City, MO", 
    city_state != "Tulsa, AL"
  ) %>% 
  filter(
    victim_race == "White" | victim_race == "Black"
  ) %>% 
  relocate(city_state)
```

2. Use the glm function for Baltimore 

```{r}

```


# Problem 3 



```{r, echo = FALSE, warning = FALSE, message = FALSE}
birth_rawdf = read_csv("./data/birthweight.csv")
```

prediction vs residuals (diff between actual and predicted); there should be no linearity because it would be a violation of the assumption

you use the model to get the predicted model to get the residual 
show rmse

Steps: 

1. Cleaned the data

```{r}
birth_cleandf = 
  birth_rawdf %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(frace),
    mrace = as.factor(mrace)
  ) %>% 
  drop_na()
```

residual plots have a line going through 0 

geom_point (hline)


2. I propose the following model:

y = b(babysex) + b(smoken) + b(wtgain) + b(smoken) + b(mrace) + b(malform) + b(wtgain) + error



```{r}
fit_mymodel = lm(bwt ~ babysex + smoken + mrace + wtgain, data = birth_cleandf)

fit_no1 = lm(bwt ~ blength + gaweeks, data = birth_cleandf)

fit_no2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex, data = birth_cleandf)
```

```{r}
fit_no1 = lm(bwt ~ blength + gaweeks, data = birth_cleandf)

fit_no2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex, data = birth_cleandf)
```
_Modeling process_

- I selected factors that I recognized from the literature may correlate to birth weight, such as maternal smoking status, maternal race, and the mother's weight gain during prenancy. I also added baby sex. 


_Plot residuals vs predictors in my model_

- the plotted residuals and predictors indicate no colinearity between my models. As such, I am content to proceed with my model. 
```{r}
birth_cleandf %>%
  add_predictions(fit_mymodel) %>% 
  add_residuals(fit_mymodel) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha = 0.5) + geom_hline(yintercept = 0)
  

```


_Identify RMSE_

fit_mymodel = lm(bwt ~ babysex + smoken + mrace + wtgain, data = birth_cleandf)

fit_no1 = lm(bwt ~ blength + gaweeks, data = birth_cleandf)

fit_no2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex, data = birth_cleandf) 

```{r}

model_df = 
  crossv_mc(birth_cleandf, 5) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
  )


model_df = 
  model_df %>% 
  mutate(
    fit_mymodel = map(.x = train, ~lm(bwt ~ babysex + smoken + mrace + wtgain, data = .x)),
    fit_no1 =    map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit_no2 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_mymodel = map2_dbl(.x = fit_mymodel, .y = test, ~rmse(model = .x, data = .y)),
    rmse_no1 =    map2_dbl(.x = fit_no1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_no2 = map2_dbl(.x = fit_no2, .y = test, ~rmse(model = .x, data = .y))
  )

```

```{r}
model_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```


As a result, I can see visually that model #2 is the better model on average as it has a lower RMSE. My model has a relatively much higher RMSE. 